MacLeish

### 2021-06-07 README.Rmd
trivial change
switch travis to github actions

[![Travis-CI Build Status](https://travis-ci.org/beanumber/macleish.svg?branch=master)](https://travis-ci.org/beanumber/macleish)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/macleish)](https://cran.r-project.org/package=macleish)

>>>>

[![R-CMD-check](https://github.com/beanumber/macleish/workflows/R-CMD-check/badge.svg)](https://github.com/beanumber/macleish/actions)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/macleish)](https://cran.r-project.org/package=macleish)
